---
title: "sepsis_eda_cleaning"
output: html_document
date: "2023-01-30"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(ggplot2)
library(forcats)
library(tidyr)
```

```{r}
df = read.csv(file = "./mods_day1_12hr.csv")
df
```

```{r}
tmp = df %>%
  group_by(EncID) %>% 
  filter(row_number()==1) %>%
  mutate(died_hr_round = floor(died_hour))

summary(tmp$died_hour)

nrow(tmp %>%
       filter(died_hr_round <=6))/
  nrow(tmp %>%
         filter(!is.na(died_hr_round)))

nrow(tmp %>%
       filter(died_hr_round <=12))/
  nrow(tmp %>%
         filter(!is.na(died_hr_round)))

ggplot(tmp, aes(x=died_hr_round)) + 
  geom_histogram(binwidth=1) +
  ggtitle('Hour from Admission to Death (MODS=1 on Day1 Patients)')+
  theme_bw()

ggplot(tmp, aes(x=died_hr_round)) + 
  geom_histogram(binwidth=1) +
  xlim(0,168) +
  ggtitle('Hour to Death 7-Day Zoom in')+
  theme_bw()

ggplot(tmp, aes(x=died_hr_round)) + 
  geom_histogram(binwidth=1) +
  xlim(0,72) +
  ggtitle('Hour to Death 3-Day Zoom in') + 
  geom_vline(xintercept = 6, color='red', linetype = "longdash") +
  geom_vline(xintercept = 12, color='blue') +
  theme_bw()

```


```{r}
age_sum = tmp %>%
  group_by(age_group) %>%
  summarise(n = n())%>%
  mutate (order = c(1,3,6,2,4,5)) %>%
  ungroup()%>%
  arrange(order)

ggplot(data=age_sum, aes(x=fct_reorder(age_group, order), y=n)) +
  geom_bar(stat="identity") +
  xlab('age_group') +
  ylab('count')+
  ggtitle('Patient in Each Age Group')+
  theme_bw()

age_sum2 = gather(tmp %>%
  group_by(age_group) %>%
  summarise(mods_day7 = sum(mods_day7)/n(),
            died_in_hosp = sum(died_in_hosp)/n())%>%
  mutate (order = c(1,3,6,2,4,5)) %>%
  ungroup()%>%
  arrange(order), key = 'count_type', value = 'value',2:3)

ggplot(data=age_sum2, aes(x=fct_reorder(age_group, order), y=value, fill=count_type)) +
  geom_bar(stat="identity", position=position_dodge()) +
  xlab('age_group') +
  ylab('proportion of age group')+
  ggtitle('Ratio of Death in Hospital and MODS Day7 per Age Group')+
  theme_bw()

age_died_time = gather(tmp %>%
  group_by(age_group) %>%
  summarise(died_time_mean = mean(died_hour,na.rm=TRUE),
            died_time_median = median(died_hour,na.rm=TRUE))  %>%
  mutate (order = c(1,3,6,2,4,5)) %>%
  ungroup()%>%
  arrange(order), key = 'statistic', value = 'value',2:3)

ggplot(data=age_died_time, aes(x=fct_reorder(age_group, order), y=value, group=statistic)) +
  geom_line(aes(color=statistic))+
  geom_point(aes(color=statistic))+
  xlab('age_group') +
  ylab('hour')+
  ggtitle('Death Time from Admission (Hr) by Age Group')+
  theme_bw()

```

```{r}
per_hr_count = df %>%
  mutate(event_hr_floor = floor(event_hour)) %>%
  group_by(event_name, event_hr_floor) %>%
  summarize(n = n_distinct(EncID)) 

ggplot(data=per_hr_count, aes(x=event_hr_floor, y=n, group=event_name)) +
  geom_line(aes(color=event_name))+
  geom_point(aes(color=event_name))+
  xlab('event_hr') +
  ylab('number of patients')+
  ggtitle('Number of Patients per Event per Hour')+
  theme_bw()

```
map = df %>%
  filter(event_name=='MAP') %>%
  mutate(event_hr_floor = floor(event_hour)) %>%
  group_by(EncID, event_hr_floor) %>%
  summarize(n = n()) %>%
  ungroup()%>%
  group_by(event_hr_floor) %>%
  summarize(mean = mean(n),
         median = median(n),
         min = min(n),
         max = max(n)) 
map

sbp = df %>%
  filter(event_name=='SBP') %>%
  mutate(event_hr_floor = floor(event_hour)) %>%
  group_by(EncID, event_hr_floor) %>%
  summarize(n = n()) %>%
  ungroup()%>%
  group_by(event_hr_floor) %>%
  summarize(mean = mean(n),
         median = median(n),
         min = min(n),
         max = max(n)) 
sbp

resp = df %>%
  filter(event_name=='RESP_RATE') %>%
  mutate(event_hr_floor = floor(event_hour)) %>%
  group_by(EncID, event_hr_floor) %>%
  summarize(n = n()) %>%
  ungroup()%>%
  group_by(event_hr_floor) %>%
  summarize(mean = mean(n),
         median = median(n),
         min = min(n),
         max = max(n)) 
resp

temp = df %>%
  filter(event_name=='TEMP') %>%
  mutate(event_hr_floor = floor(event_hour)) %>%
  group_by(EncID, event_hr_floor) %>%
  summarize(n = n()) %>%
  ungroup()%>%
  group_by(event_hr_floor) %>%
  summarize(mean = mean(n),
         median = median(n),
         min = min(n),
         max = max(n)) 
temp

sf = df %>%
  filter(event_name=='SF_RATIO') %>%
  mutate(event_hr_floor = floor(event_hour)) %>%
  group_by(EncID, event_hr_floor) %>%
  summarize(n = n()) %>%
  ungroup()%>%
  group_by(event_hr_floor) %>%
  summarize(mean = mean(n),
         median = median(n),
         min = min(n),
         max = max(n)) 
sf
```

```{r}
```


